Ants-Review: an Ethereum-Based Privacy-Oriented Protocol for Incentivized Open Peer Reviews

### 2020-11-23 article.tex
Latest commits.

\title{Ants-Review: an Ethereum-Based Privacy-oriented Protocol for Incentivized Open Peer Reviews}

@@

\subsubsection{Declaration of Competing Interest}
This work was developed during the ETHTurin Hackathon 2020 and the Kernel Fellowship program 2020. These organizations had no financial role in the design and implementation of this protocol.

>>>>

\title{Ants-Review: an Ethereum-Based Privacy-Oriented Protocol for Incentivized Open Peer Reviews}

@@

\subsubsection{Declaration of Competing Interest}
This work was mainly developed during the ETHTurin Hackathon 2020 and the Gitcoin Kernel Fellowship program 2020. These organizations, as well as the authors' affiliations, had no financial role in the design and implementation of the protocol.
